\vskip-0.6in Trade Agreements in the Shadow of Lobbying\protect\footnote{Formerly circulated under the title ``Trade Agreements, Lobbying and Separation of Powers''}

### 2016-01-29 draft.tex
add game-tree.tex and start of code for extensive form into draft.tex

@@

>>>>

\usepackage{tikz}
\tikzset{
% Two node styles for game trees: solid and hollow
solid node/.style={circle,draw,inner sep=1.5,fill=black},
hollow node/.style={circle,draw,inner sep=1.5,fill=white}
%non node/.style={circle,draw,inner sep=.1,fill=black}
}

@@

\begin{figure}
\begin{center}
\begin{tikzpicture}[scale=1.5,font=\footnotesize, grow=right]
% Specify spacing for each level of the tree
\tikzstyle{level 1}=[level distance=10mm,sibling distance=10mm]
\tikzstyle{level 2}=[level distance=10mm,sibling distance=10mm]
% The Tree
\node(0)[solid node,label=above:{$E,E^*$}]{} 
child{node(1)[solid node,label=below:{$0$}]{}
}
child{[white] node(2)[solid node,xshift=12]{}  %note that you need to adjust the yshift if you change the sibling distance
child{[black] node(4)[solid node,label=below:{$0$}]{}
}
child{[white] node(7)[hollow node,xshift=12]{}  %note that you need to adjust the yshift if you change the sibling distance
child{[black] node(9)[solid node,label=below:{$0$}]{} }
child{[black] node(11)[solid node,label=above:{$\infty$}]{} }
 edge from parent node[black, xshift=23]{$e_b$} %note that you need to adjust the yshift if you change the level distance
}
child{[black] node(6)[solid node,label=above:{$\infty$}]{}}
 edge from parent node[black, xshift=23]{$\bta$} %note that you need to adjust the yshift if you change the level distance
}
child{node(3)[solid node,label=above:{$\infty$}]{}
}
;
% information set
    \draw[solid,bend right](1)to(3);
		\draw[solid,bend right](4)to(6);
		\draw[solid,bend right](9)to(11);

\end{tikzpicture}

\end{center}
\caption{Extensive Form\label{fig:ext}}
\end{figure}
